---
format:
  html:
    toc: false
---
::: {.film-grain}
:::


```{r setup}
#| echo: false

add_scene <- function(src, title, role, text, url, link_text, img_alt, direction = "right") {
  lines <- c(
    sprintf('<div class="scene-wrapper scroll-reveal" data-direction="%s">', direction),
    '<div class="scene">',
    paste0(
      '<div class="scene-visual">',
      '<div class="image-container">',
      '<img src="', src, '" alt="', img_alt, '" class="portrait">',
      '<div class="vignette"></div>',
      '</div>',
      '</div>'
    ),
    '<div class="scene-details">',
    paste0('<h2 class="character-name">', title, '</h2>'),
    paste0('<div class="role">', role, '</div>'),
    '<div class="separator"></div>',
    paste0('<div class="character-arc text-justify">', text, '</div>'),
    paste0('<a href="', url, '" class="credits-link" target="_blank">', 
           '<span class="link-text">', link_text, '</span>',
           '<span class="link-line"></span>',
           '</a>'),
    '</div>',
    '</div>',
    '</div>'
  )
  cat(lines, sep="\n")
}
```

::: {.film-reel}
::: {.content-visible when-profile="english"}
```{r english-team}
#| echo: false
#| results: asis

# First team member
add_scene(
  src = "images/avatar-rani.png",
  title = "Rani", 
  role = "Director & Creator",
  text = "Rani got into filmmaking while studying film in Seoul, South Korea. He now works as a freelance translator and spends his free time creating music - or noise - on the piano or computer, playing video games late into the night, and immersing himself in literature and philosophy. He is particularly interested in discovering new experiences and impressions through various forms of art and media, and wishes to convey this through his own work.",
  url = "https://www.swissfilms.ch/en/person/gillioz-rani/320F8A74646E41718A8CB4BD0C32B79A",
  img_alt = "An avatar of a man with a beard.",
  link_text = "View Portfolio",
  direction = "right"
)

# Second team member
add_scene(
  src = "images/vincent_profile.jpg",
  title = "Vincent", 
  role = "President & Creator",
  text = "Meet Vincent, our storyteller. His love for spinning tales began long ago, first as an English and History teacher, where he wove narratives into every lesson. But Vincent didn't stop there; he took his storytelling prowess to the airwaves, crafting podcasts designed to be both educational and entertaining. With a penchant for psychological thrillers and the allure of unanswered questions, Vincent is an avid consumer of cultural media.",
  url = "https://www.linkedin.com/in/vincent-lettry-a4ab81259/",
  img_alt = "An avatar of a blond man.",
  link_text = "View Portfolio",
  direction = "left"
)

# Third team member
add_scene(
  src = "images/matthias_profile.jpeg",
  title = "Matthias", 
  role = "Creator",
  text = "Working mainly as a modern art dealer with a background in filmaking, ranging from film analysis to screenwriting as well as acting, Matthias' intend is to merge his array of skills for the benefit of helping the creation of original works, free of conventions and pre-made ideas.",
  url = "https://ersatzproduction.com",
  img_alt = "Matthias profile photo",
  link_text = "View Portfolio",
  direction = "right"
)

# Fourth team member
add_scene(
  src = "images/lclettry_profile.jpg",
  title = "Layal", 
  role = "Technology & Organisation",
  text = "Layal is passionate about s, whether living, dead or computer-based. After graduating from high school with a focus on s and philosophy, she went on to study Management and Economics, during which time she developed a passion for statistics and econometrics. After working in the Swiss federal administration as an econometrician, she decided to concentrate on data processing. She then became a consultant in R  as a data scientist. Thanks to her IT and data management skills, she is mainly responsible for maintaining the production company's IT solutions and finances.",
  url = "https://lclettry.com",
  img_alt = "A girl.",
  link_text = "View Portfolio",
  direction = "left"
)   

```
:::
::: {.content-visible when-profile="french"}
```{r french-team}
#| echo: false
#| results: asis

# First team member
 add_scene(
  src = "images/avatar-rani.png",
  title = "Rani", 
  role = "Réalisateur & Créateur",
  text = "Rani s'est lancé dans la réalisation de films en étudiant le cinéma à Séoul, en Corée du Sud. Il travaille aujourd'hui comme traducteur indépendant et passe son temps libre à créer de la musique – ou du bruit – au piano ou à l'ordinateur, à jouer aux jeux vidéo jusque tard dans la nuit, et à s'immerger dans la littérature et la philosophie. Il s'intéresse en particulier à la découverte de nouvelles expériences et impressions à travers diverses formes d'art et de médias, et souhaite transmettre cela à travers ses propres oeuvres.",
  url = "https://www.swissfilms.ch/en/person/gillioz-rani/320F8A74646E41718A8CB4BD0C32B79A",
  img_alt = "Un avatar d'un homme barbu.",
  link_text = "Voir le portfolio",
  direction = "right"
)

# Second team member
add_scene(
  src = "images/vincent_profile.jpg",
  title = "Vincent", 
  role = "Président & Créateur",
  text = "Rencontre Vincent, notre narrateur. Son amour pour les histoires a commencé il y a longtemps, d'abord en tant qu'enseignant d'anglais et de histoire, où il a tissé des histoires dans chaque leçon. Mais Vincent n'a pas arrêté là; il a porté sa maîtrise du récit à la radio, créant des podcasts conçus à la fois pour être éducatifs et amusants. Avec un penchant pour les thrillers psychologiques et l'allure des questions sans réponse, Vincent est un avid consumer de médias culturels.",
  url = "https://www.linkedin.com/in/vincent-lettry-a4ab81259/",
  img_alt = "Un avatar d'un blond.",
  link_text = "Voir le portfolio",
  direction = "left"
)

# Third team member
add_scene(
  src = "images/matthias_profile.jpeg",
  title = "Matthias", 
  role = "Créateur",
  text = "Travaillant principalement comme commerçant d'art moderne avec une formation en cinéma, allant de l'analyse de film à la rédaction de scénarios, Matthias souhaite fusionner ses compétences pour aider à la création de nouvelles œuvres, libres de conventions et d'idées pré-conçues.",
  url = "https://ersatzproduction.com",
  img_alt = "Matthias profile photo",
  link_text = "Voir le portfolio",
  direction = "right"
)

# Fourth team member
add_scene(  
  src = "images/lclettry_profile.jpg",    
  title = "Layal",
  role = "Technologie & Organisation",
  text = "Layal est passionnée par les langues, qu'elles soient vivantes, mortes ou informatiques. Après avoir obtenu une maturité gymnasiale centrée sur les langues et la philosophie, elle se lance dans des études de gestion d'entreprise et d'économie politique, pendant lesquelles elle développe une passion pour la statistique et l'économétrie. Après avoir travaillé au sein de l'administration fédérale suisse en tant qu'économètre, elle décide de se concentrer sur le traitement des données. Elle devient alors consultante en langage R en tant que scientifique des données. Grâce à ses compétences informatiques et de gestion des données, elle s'occupe principalement de la maintenance des solutions informatiques et des finances de la société de production.",
  url = "https://lclettry.com",
  img_alt = "Une fille.",
  link_text = "Voir le portfolio",
  direction = "left"
)
```
:::
:::

<script>
// Wait for the HTML document to be fully loaded
document.addEventListener('DOMContentLoaded', function() {
    const scenes = document.querySelectorAll('.scroll-reveal');
    
    // Function to check if device is mobile
    const isMobile = () => window.innerWidth <= 768;
    
    const observer = new IntersectionObserver((entries) => {
        entries.forEach(entry => {
            if (entry.isIntersecting) {
                const element = entry.target;
                element.style.opacity = "1";
                
                // On mobile, always slide up instead of left/right
                if (isMobile()) {
                    element.style.transform = "translateY(0)";
                } else {
                    element.style.transform = "translateX(0)";
                }
            }
        });
    }, {
        threshold: 0.2,
        rootMargin: '0px'
    });

    // Update initial transform based on device
    scenes.forEach(scene => {
        if (isMobile()) {
            scene.style.transform = "translateY(50px)";
        } else {
            const direction = scene.dataset.direction;
            scene.style.transform = `translateX(${direction === 'right' ? '100px' : '-100px'})`;
        }
        observer.observe(scene);
    });
    
    // Handle resize events
    window.addEventListener('resize', () => {
        scenes.forEach(scene => {
            if (isMobile()) {
                scene.style.transform = "translateY(50px)";
            } else {
                const direction = scene.dataset.direction;
                scene.style.transform = `translateX(${direction === 'right' ? '100px' : '-100px'})`;
            }
        });
    });
});
</script>
