---
title: "The Crew"
format:
  html:
    css: styles.css
    toc: false
---

::: {.film-grain}
:::

::: {.opening-credits}
::: {.title-card}
# [ERSATZ]{.company-name} [PRODUCTION]{.company-type}
::: {.tagline}
::: {.content-visible when-profile="english"}
Presents
::: {.content-visible when-profile="french"}
Présente
:::
:::
:::
:::

```{r setup}
#| echo: false
add_scene <- function(src, title, role, text, url, link_text, img_alt, direction = "right") {
  lines <- c(
    sprintf('<div class="scene-wrapper scroll-reveal" data-direction="%s">', direction),
    '<div class="scene">',
    paste0(
      '<div class="scene-visual">',
      '<div class="image-container">',
      '<img src="', src, '" alt="', img_alt, '" class="portrait">',
      '<div class="vignette"></div>',
      '</div>',
      '</div>'
    ),
    '<div class="scene-details">',
    paste0('<h2 class="character-name">', title, '</h2>'),
    paste0('<div class="role">', role, '</div>'),
    '<div class="separator"></div>',
    paste0('<div class="character-arc text-justify">', text, '</div>'),
    paste0('<a href="', url, '" class="credits-link" target="_blank">', 
           '<span class="link-text">', link_text, '</span>',
           '<span class="link-line"></span>',
           '</a>'),
    '</div>',
    '</div>',
    '</div>'
  )
  cat(lines, sep="\n")
}
```

::: {.film-reel}
```{r}
#| echo: false
#| results: asis

# First team member
add_scene(
  src = "images/avatar-rani.png",
  title = "Rani", 
  role = "Director & Creator",
  text = "Rani embarked on his discovery of filmmaking by studying cinema in Seoul, South Korea. Now working as a freelance translator, he spends his free time creating music – or noise – on the piano or computer, gaming late into the night, and delving into literature and philosophy. The discovery of new experiences and impressions through diverse art forms and media is what interests him and what he wishes to convey through his own works.",
  url = "https://www.swissfilms.ch/en/person/gillioz-rani/320F8A74646E41718A8CB4BD0C32B79A",
  img_alt = "An avatar of a man with a beard.",
  link_text = "View Portfolio",
  direction = "right"
)

# Second team member
add_scene(
  src = "images/vincent_profile.jpg",
  title = "Vincent", 
  role = "President & Creator",
  text = "Meet Vincent, our resident storyteller. His love for spinning tales began long ago, first as an English and History teacher, where he wove narratives into every lesson. But Vincent didn't stop there; he took his storytelling prowess to the airwaves, crafting podcasts designed to be both educational and entertaining. With a penchant for psychological thrillers and the allure of unanswered questions, Vincent is an avid consumer of cultural media.",
  url = "https://www.linkedin.com/in/vincent-lettry-a4ab81259/",
  img_alt = "An avatar of a blond man.",
  link_text = "View Portfolio",
  direction = "left"
)

# Third team member
add_scene(
  src = "images/matthias_profile.jpeg",
  title = "Matthias", 
  role = "Creator",
  text = "Working mainly as a modern art dealer with a background in filmaking, ranging from film analysis to screenwriting as well as acting, Matthias' intend is to merge his array of skills for the benefit of helping the creation of original works, free of conventions and pre-made ideas.",
  url = "https://ersatzproduction.com",
  img_alt = "Matthias profile photo",
  link_text = "View Portfolio",
  direction = "right"
)

# Fourth team member
add_scene(
  src = "images/lclettry_profile.jpg",
  title = "Layal", 
  role = "Technology & Organisation",
  text = "Meet Layal, our data magician! She's all about bringing data to life with a dash of creativity and a sprinkle of magic. Enjoying animated and superhero movies, Layal's passion shines through in her work as a data scientist and econometrician. Whether she's jazzing up our website or keeping our accounts in check, Layal's got the knack for making things look good and run smoothly.",
  url = "https://lclettry.com",
  img_alt = "A girl.",
  link_text = "View Portfolio",
  direction = "left"
)
```
:::

<script>
// Wait for the HTML document to be fully loaded
document.addEventListener('DOMContentLoaded', function() {
    const scenes = document.querySelectorAll('.scroll-reveal');
    
    // Function to check if device is mobile
    const isMobile = () => window.innerWidth <= 768;
    
    const observer = new IntersectionObserver((entries) => {
        entries.forEach(entry => {
            if (entry.isIntersecting) {
                const element = entry.target;
                element.style.opacity = "1";
                
                // On mobile, always slide up instead of left/right
                if (isMobile()) {
                    element.style.transform = "translateY(0)";
                } else {
                    element.style.transform = "translateX(0)";
                }
            }
        });
    }, {
        threshold: 0.2,
        rootMargin: '0px'
    });

    // Update initial transform based on device
    scenes.forEach(scene => {
        if (isMobile()) {
            scene.style.transform = "translateY(50px)";
        } else {
            const direction = scene.dataset.direction;
            scene.style.transform = `translateX(${direction === 'right' ? '100px' : '-100px'})`;
        }
        observer.observe(scene);
    });
    
    // Handle resize events
    window.addEventListener('resize', () => {
        scenes.forEach(scene => {
            if (isMobile()) {
                scene.style.transform = "translateY(50px)";
            } else {
                const direction = scene.dataset.direction;
                scene.style.transform = `translateX(${direction === 'right' ? '100px' : '-100px'})`;
            }
        });
    });
});
</script>
